Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-03 latex/comp_or.tex
Paper update

\begin{table}[H]
	\centering
	\caption{Air cargo transport: literature, problems and features}  \label{tab:sa}
	\scriptsize
	\renewcommand{\arraystretch}{1.1} % alturas das linhas \specialcell{{\bf Parallel}\\{\bf heuristics}}
	\begin{tabular}{r|cc|cc|cc|ccc|c}
		\toprule
		                            & {\bf APP}  & {\bf WBP}  &  {\bf SPDP}   &{\bf TSP}   & {\bf 2D}  & {\bf 3D}  & {\bf Heu}  & {\bf Int}  & {\bf Lin} & \specialcell{{\bf Parallel}\\{\bf heuristics}}\\
		\midrule
		\cite{LarsenMikkelsen1979}  & $.$        & $\bigstar$ & $.$          & $.$        & $.$       & $.$       & $\bigstar$ & $.$        &  $.$&  $.$ \\
		\cite{Brosh1981}  & $.$ & $\bigstar$  & $.$   & $.$ & $.$ & $.$   & $.$  & $.$  &  $\bigstar$&  $.$ \\
		\cite{Kevin1992}  & $.$ & $\bigstar$  & $.$ & $.$ & $.$ &$.$   & $.$  & $\bigstar$  &  $.$ &  $.$\\
		\cite{Heidelberg1998}  & $.$ & $\bigstar$  & $.$ & $.$ & $\bigstar$ &$.$   & $\bigstar$  & $.$  &  $.$&  $.$ \\
		\cite{MongeauBes2003}    & $\bigstar$ & $\bigstar$   & $.$ & $.$ & $.$ & $.$   & $.$  & $\bigstar$  &  $.$ &  $.$\\
		\cite{fok2004optimizing} & $.$ & $\bigstar$   & $.$ & $.$ & $.$ & $.$   & $.$  & $\bigstar$  &  $.$&  $.$ \\	
		\cite{Chan2006}  & $\bigstar$ & $.$    & $.$ & $.$ & $.$ & $\bigstar$  & $\bigstar$  & $.$  &  $.$&  $.$ \\
		\cite{KaluznyBohdanL2009Oalb}  & $.$ & $\bigstar$  & $.$  & $.$ & $\bigstar$ &$.$  & $.$  & $\bigstar$  &  $.$&  $.$ \\
		\cite{Verstichel2011}   & $.$ & $\bigstar$    & $.$ & $.$ & $.$ & $.$   & $.$  & $\bigstar$  &  $.$&  $.$ \\
		\cite{MesquitaCunha2011}   & $.$ & $.$    & $\bigstar$ & $.$ & $.$ & $.$   & $\bigstar$  & $.$  &  $.$ &  $.$\\		
		\cite{Limbourg2012} & $.$ & $\bigstar$  & $.$ & $.$ & $.$ & $.$   & $.$  & $\bigstar$  &  $.$&  $.$ \\

		\cite{kaspi2019} & $.$ & $.$  & $.$ & $\bigstar$ & $.$ & $.$   & $\bigstar$  & $.$  &  $.$&  $.$ \\

		\cite{RoesenerHall2014}  & $\bigstar$ & $\bigstar$  & $.$  & $.$ & $.$ & $\bigstar$   & $.$  & $\bigstar$  &  $.$&  $.$ \\
		\cite{Vancroonemburg2014}  & $\bigstar$ & $\bigstar$   & $.$ & $.$ & $.$ & $.$   & $.$  & $\bigstar$  &  $.$&  $.$ \\
		\cite{LurkinSchyns2015} & $.$ & $\bigstar$  & $\bigstar$ & $.$  & $.$ & $.$   & $.$  & $\bigstar$  &  $.$&  $.$ \\
		\cite{RoesenerBarnes2016}  & $.$ & $\bigstar$   & $.$ & $.$ & $.$ & $.$   & $\bigstar$  & $.$  &  $.$&  $.$ \\
		\cite{PaquaySchynsLimbourg2016,PaquayLimbourgSchynsOliveira2018}  & $\bigstar$ & $\bigstar$ & $.$ & $.$ & $.$ & $\bigstar$ & $\bigstar$  & $\bigstar$ & $.$&  $.$ \\
		\cite{YangLiuGao2018} & $.$ & $\bigstar$  & $.$  & $.$ & $\bigstar$  & $.$ & $\bigstar$ & $.$  & $.$&  $.$ \\
		\cite{wong2020} & $\bigstar$  & $\bigstar$  & $.$  & $.$   & $.$  & $.$ & $.$ & $\bigstar$  & $.$&  $.$  \\
		\cite{eugene2021} & $\bigstar$ & $\bigstar$ & $.$  & $.$   & $.$ & $.$ & $.$ & $\bigstar$  & $.$&  $.$  \\
		\cite{zhao2021} & $.$ & $\bigstar$ & $.$  & $.$  & $.$ & $.$ & $.$  & $\bigstar$ &  $.$&  $.$ \\

		\cite{MesquitaSanches2023}   & $\bigstar$ & $\bigstar$  & $\bigstar$& $\bigstar$ & $.$ & $.$ & $\bigstar$ & $\bigstar$   &  $.$&  $.$  \\

		{\bf This work}   & $\bigstar$ & $\bigstar$  & $\bigstar$& $\bigstar$ & $.$ & $.$ & $\bigstar$ & $\bigstar$   &  $.$&  $\bigstar$  \\
		\bottomrule 
	\end{tabular}
	\normalsize 
\end{table}

As can be seen, so far \cite{LurkinSchyns2015} is the only work that simultaneously addresses an air cargo (WBP) and a flight itinerary (PDP) sub-problem. Although it is innovative, strong simplifications were imposed by the authors: in relation to loading, APP was ignored; with regard to routing, it is assumed a pre-defined flight plan restricted to two legs. It is important to note that these authors consider an aircraft with two doors, and the minimization of loading and unloading costs at the intermediate node was modelled through a container sequencing problem. Referring directly to this work, \cite[p. 409]{BrandtStefan2019} comment: {\it However, not even these sub-problems are acceptably solved for real-world problem sizes or the models omit some practically relevant constraints}.

>>>>

\begin{table}[H]
	\centering
	\caption{Air cargo transport: literature, problems and features}  \label{tab:sa}
	\scriptsize
	\renewcommand{\arraystretch}{1.1} % alturas das linhas \specialcell{{\bf Parallel}\\{\bf heuristics}}
	\begin{tabular}{r|ccc|cc|cc|ccc|c}
		\toprule
		                            & {\bf APP}  & {\bf WBP}   & {\bf MLU} &{\bf SPDP}&{\bf TSP} & {\bf 2D} & {\bf 3D} & {\bf Heu} & {\bf Int}  & {\bf Lin} & \specialcell{{\bf Parallel}\\{\bf heuristics}}\\
		\midrule
		\cite{LarsenMikkelsen1979}  & $.$        & $\bigstar$  & $.$       & $.$      & $.$      & $.$      & $.$      & $\bigstar$& $.$        &  $.$       &  $.$ \\
		\cite{Brosh1981}            & $.$        & $\bigstar$  & $.$       & $.$      & $.$      & $.$      & $.$      & $.$       & $.$        &  $\bigstar$&  $.$ \\
		\cite{Kevin1992}            & $.$        & $\bigstar$  & $.$       & $.$      & $.$      & $.$      & $.$      & $.$       & $\bigstar$ &  $.$       &  $.$\\
		\cite{Heidelberg1998}       & $.$        & $\bigstar$  & $.$       & $.$      & $.$      &$\bigstar$& $.$      & $\bigstar$& $.$        &  $.$       &  $.$ \\
		\cite{MongeauBes2003}       & $\bigstar$ & $\bigstar$  & $.$       & $.$      & $.$      & $.$      & $.$      & $.$       & $\bigstar$ &  $.$       &  $.$\\
		\cite{fok2004optimizing}    & $.$        & $\bigstar$  & $.$       & $.$      & $.$      & $.$      & $.$      & $.$       & $\bigstar$ &  $.$       &  $.$ \\	
		\cite{Chan2006}             & $\bigstar$ & $.$         & $.$       & $.$      & $.$      & $.$      &$\bigstar$& $\bigstar$& $.$        &  $.$       &  $.$ \\
		\cite{KaluznyBohdanL2009Oalb}& $.$       & $\bigstar$  & $.$       & $.$      & $.$      &$\bigstar$& $.$      & $.$       & $\bigstar$ &  $.$       &  $.$ \\
		\cite{Verstichel2011}       & $.$        & $\bigstar$  & $.$       & $.$      & $.$      & $.$      & $.$      & $.$       & $\bigstar$ &  $.$       &  $.$ \\
		\cite{MesquitaCunha2011}    & $.$        & $.$         & $.$       &$\bigstar$& $.$      & $.$      & $.$      & $\bigstar$& $.$        &  $.$       &  $.$ \\		
		\cite{Limbourg2012}         & $.$        & $\bigstar$  & $.$       & $.$      & $.$      & $.$      & $.$      & $.$       & $\bigstar$ &  $.$       &  $.$ \\

		\cite{kaspi2019}            & $.$        & $.$         & $.$       & $.$      &$\bigstar$& $.$      & $.$      &$\bigstar$ & $.$        &  $.$       &  $.$ \\

		\cite{RoesenerHall2014}     & $\bigstar$ & $\bigstar$  & $.$       & $.$      & $.$      & $.$      &$\bigstar$& $.$       & $\bigstar$ &  $.$       &  $.$ \\
		\cite{Vancroonemburg2014}   & $\bigstar$ & $\bigstar$  & $.$       & $.$      & $.$      & $.$      & $.$      & $.$       & $\bigstar$ &  $.$       &  $.$ \\
		\cite{LurkinSchyns2015}     & $.$        & $\bigstar$  & $\bigstar$&$\bigstar$& $.$      & $.$      & $.$      & $.$       & $\bigstar$ &  $.$       &  $.$ \\
		\cite{RoesenerBarnes2016}   & $.$        & $\bigstar$  & $.$       & $.$      & $.$      & $.$      & $.$      & $\bigstar$& $.$        &  $.$       &  $.$ \\

		\cite{PaquaySchynsLimbourg2016,PaquayLimbourgSchynsOliveira2018}&$\bigstar$&$.$&$.$&$.$&$.$&$.$     &$\bigstar$&$\bigstar$ & $\bigstar$&$\bigstar$  &  $.$ \\

		\cite{YangLiuGao2018}       & $.$        & $\bigstar$  & $.$       & $.$      & $.$      &$\bigstar$& $.$      & $\bigstar$ & $.$       & $.$        &  $.$ \\
		\cite{wong2020}             & $\bigstar$ & $\bigstar$  & $.$       & $.$      & $.$      & $.$      & $.$      & $.$        & $\bigstar$& $.$        &  $.$  \\
		\cite{eugene2021}           & $\bigstar$ & $\bigstar$  & $.$       & $.$      & $.$      & $.$      & $.$      & $.$        & $\bigstar$& $.$        &  $.$  \\
		\cite{zhao2021}             & $.$        & $\bigstar$  & $.$       & $.$      & $.$      & $.$      & $.$      & $.$        & $\bigstar$&  $.$       &  $.$ \\

		\cite{MesquitaSanches2023}  & $\bigstar$ & $\bigstar$  & $.$       &$\bigstar$&$\bigstar$& $.$      & $.$      & $\bigstar$ & $\bigstar$&  $.$       &  $.$  \\

		{\bf This work}             & $\bigstar$ & $\bigstar$  &$\bigstar$ &$\bigstar$&$\bigstar$& $.$      & $.$      & $\bigstar$ & $\bigstar$&  $.$       &  $\bigstar$  \\
		\bottomrule 
	\end{tabular}
	\normalsize 
\end{table}

As can be seen, so far \cite{LurkinSchyns2015} is the only work that simultaneously addresses an air cargo (WBP) and a flight itinerary (PDP) sub-problem. Although it is innovative, strong simplifications were imposed by the authors: in relation to loading, APP was ignored; with regard to routing, it is assumed a pre-defined flight plan restricted to two legs. It is important to note that these authors consider an aircraft with two doors, and the minimization of loading and unloading (MLU) costs at the intermediate node was modelled through a container sequencing problem. Referring directly to this work, \cite[p. 409]{BrandtStefan2019} comment: {\it However, not even these sub-problems are acceptably solved for real-world problem sizes or the models omit some practically relevant constraints}.
